---
title: "Problem 32"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Pandigital products

We shall say that an $n$-digit number is pandigital if it makes use of all the digits $1$ to $n$ exactly once; for example, the $5$-digit number, $15234$, is $1$ through $5$ pandigital.

The product $7254$ is unusual, as the identity, $39 \times 186 = 7254$, containing multiplicand, multiplier, and product is $1$ through $9$ pandigital.

Find the sum of all products whose multiplicand/multiplier/product identity can be written as a $1$ through $9$ pandigital.

HINT: Some products can be obtained in more than one way so be sure to only include it once in your sum.

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function(k) {
    digits <- as.character(1:9)
    possible_numbers <- list(NULL, NULL, NULL, list(c(1, 1)), list(c(1, 2)), list(c(1, 2)), list(c(1, 3), c(2, 2)),
                             list(c(1, 3), c(2, 2)), list(c(1, 4), c(2, 3)))
    products <- NULL
    for (i in possible_numbers[[k]]) {
        multiplicands <- as.matrix(expand.grid(rep(list(digits), i[1]), stringsAsFactors = FALSE))
        for (n in seq_len(nrow(multiplicands))) {
            if (length(unique(multiplicands[n, ])) == i[1]) {
                multipliers <- as.matrix(expand.grid(rep(list(digits[!digits %in% multiplicands[n, ]]), i[2]),
                                                     stringsAsFactors = FALSE))
                for (m in seq_len(nrow(multipliers))) {
                    if (length(unique(multipliers[m, ])) == i[2]) {
                        product <- as.integer(paste0(multiplicands[n, ], collapse = "")) * as.integer(paste0(multipliers[m, ], collapse = ""))
                        check_digits <- sort(c(multiplicands[n, ], multipliers[m, ],
                                               strsplit(as.character(product), NULL)[[1]]))
                        if (length(check_digits) == k && all(check_digits == digits)) products <- c(products, product)
                    }
                }
            }
        }
    }
    return(sum(unique(products)))
}

```
```{r}
compute(9)
```
```{r}
microbenchmark(compute(9))
```
