---
title: "Problem 50"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Consecutive prime sum

The prime $41$, can be written as the sum of six consecutive primes:

$$41 = 2 + 3 + 5 + 7 + 11 + 13$$

This is the longest sum of consecutive primes that adds to a prime below one-hundred.

The longest sum of consecutive primes below one-thousand that adds to a prime, contains $21$ terms, and is equal to $953$.

Which prime, below one-million, can be written as the sum of the most consecutive primes?

OEIS Sequence: [A013918](https://oeis.org/A013918)

## Solution
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```
```{r}
compute <- function(n) {
    sieve <- prime_sieve(n)
    primes <- which(sieve)
    max_sequence <- 0; max_sequence_sum <- 0
    for (i in primes) {
        max_sequence_sum <- max_sequence_sum + i
        if (max_sequence_sum < n) max_sequence <- max_sequence + 1 else break
    }
    for (i in max_sequence:0) {
        for (j in seq_len(length(primes) - i + 1)) {
            sum_sequence <- sum(primes[j:(i + j)])
            if (sum_sequence > n) {
                break
            } else if (sieve[sum_sequence]) {
                return(sum_sequence)
            }
        }
    }
}
```
```{r}
compute(100)
```
```{r}
compute(1000)
```
```{r}
compute(1000000)
```
```{r}
microbenchmark(compute(1000000))
```
