---
title: "Problem 12"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Highly divisible triangular number
The sequence of triangle numbers is generated by adding the natural numbers. So the $7$th triangle number would be $1 + 2 + 3 + 4 + 5 + 6 + 7 = 28$. The first ten terms would be:

$$1, 3, 6, 10, 15, 21, 28, 36, 45, 55, ...$$

Let us list the factors of the first seven triangle numbers:

$$1 : 1$$

$$3 : 1, 3$$

$$6 : 1, 2, 3, 6$$

$$10 : 1, 2, 5, 10$$

$$15 : 1, 3, 5, 15$$

$$21 : 1, 3, 7, 21$$

$$28 : 1, 2, 4, 7, 14, 28$$

We can see that $28$ is the first triangle number to have over five divisors. What is the value of the first triangle number to have over five hundred divisors?

## Solution
We need only prime factorization to get number of divisors.
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/numbers.R")
```
```{r}
compute <- function (n) {
    i <- 1
    triangle <- 1
    while (count_divisors(triangle) < n) {
        i <- i + 1
        triangle <- triangle + i
    }
    return(triangle)
}
```
```{r}
compute(5)
```
```{r}
compute(500)
```
```{r}
microbenchmark(compute(500))
```
