---
title: "Problem 14"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Longest Collatz sequence
The following iterative sequence is defined for the set of positive integers:

$$n = \begin {cases} \displaystyle \frac {n}{2} & \quad \text {if } n \text { is even}\\ 3 \times n + 1 & \quad \text {if } n \text { is odd}\end {cases}$$

Using the rule above and starting with $13$, we generate the following sequence:

$$13 \to 40 \to 20 \to 10 \to 5 \to 16 \to 8 \to 4 \to 2 \to 1$$

It can be seen that this sequence (starting at $13$ and finishing at $1$) contains $10$ terms. Although it has not been proved yet (Collatz Problem), it is thought that all starting numbers finish at $1$.

Which starting number, under one million, produces the longest chain?

**NOTE**: Once the chain starts the terms are allowed to go above one million.

## Solution
For decreasing number of iterations we could use memoization. Also we can skip one step when $n$ is odd 'coz if $n$ is odd then $3n+1$ always even.
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/calculus.R")
```
```{r}
compute <- function(n) {
    result <- 0
    max_chain <- 0
    len_collatz_chain <- len_collatz_chain()
    for (i in 1:(n - 1)) {
        if (len_collatz_chain(i) > max_chain) {
            max_chain <- len_collatz_chain(i)
            result <- i
        }
    }
    return(result)
}
```
```{r}
compute(1000000)
```
```{r}
microbenchmark(compute(1000000))
```