---
title: "Problem 37"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Truncatable primes

The number $3797$ has an interesting property. Being prime itself, it is possible to continuously remove digits from left to right, and remain prime at each stage: $3797, 797, 97$, and $7$. Similarly we can work from right to left: $3797, 379, 37$, and $3$.

Find the sum of the only eleven primes that are both truncatable from left to right and right to left.

NOTE: $2, 3, 5$, and $7$ are not considered to be truncatable primes.

OEIS Sequence: [A020994](https://oeis.org/A020994)

## Solution

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```
```{r}
compute <- function() {
    sieve <- prime_sieve(1000000)
    primes <- which(sieve)[-(1:4)]
    truncatable <- 0; result <- 0
    for (prime in primes) {
        p <- 10; is.trunctatable <- TRUE
        while (p < prime) {
            if (sieve[prime %% p] && sieve[prime %/% p]) {
                p <- p * 10
            } else {
                is.trunctatable <- FALSE
                break
            }
        }
        if (is.trunctatable) {
            truncatable <- truncatable + 1
            result <- result + prime
            if (truncatable == 11) break
        }
    }
    return(result)
}
```
```{r}
compute()
```
```{r}
microbenchmark(compute())
```
