---
title: "Problem 650"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Divisors of Binomial Product

Let $\displaystyle B(n) = \prod_{k = 0}^n \binom{n}{k}$, a product of binomial coefficients.

For example, $\displaystyle B(5) = \binom{5}{0} \times \binom{5}{1} \times \binom{5}{2} \times \binom{5}{3} \times \binom{5}{4} \times \binom{5}{5} = 1 \times 5 \times 10 \times 10 \times 5 \times 1 = 2500$.

Let $\displaystyle D(n) = \sum_{d | B(n)} d$, the sum of the divisors of $B(n)$.

For example, the divisors of $B(5)$ are $1$, $2$, $4$, $5$, $10$, $20$, $25$, $50$, $100$, $125$, $500$, $625$, $1250$ and $2500$, so $D(5) = 1 + 2 + 4 + 5 + 10 + 20 + 25 + 50 + 100 + 125 + 250 + 500 + 625 + 1250 + 2500 = 5467$.

Let $\displaystyle S(n) = \sum_{k = 1}^n D(k)$,

You are given $S(5) = 5736$, $S(10) = 141740594713218418$ and $S(100) \mod 1000000007 = 332792866$.

Find $S(20000) \mod 1000000007$.

## Solution

The product of binomial coefficients could be written as:

$$\prod_{k = 0}^n \binom{n}{k} = \prod_{k = 0}^n k ^ {2k - n - 1} = \frac{1 ^ 1 \times 2 ^ 2 \times 3 ^ 3 \times ... \times n ^ n}{1! \times 2! \times 3! \times ... \times n!} = \prod_{k = 0}^n \frac{k ^ k}{k!}$$

If $n$ is a power of a prime number $p$, then sum of all divisors of $n$ is $\sigma(n)$:

$$\sigma(n) = \frac{p ^ {k + 1} - 1}{p - 1}$$.

For example:

$$B(5) = \frac{1 ^ 1 \times 2 ^ 2 \times 3 ^ 3 \times 4 ^ 4 \times 5 ^ 5}{1! \times 2! \times 3! \times 4! \times 5!} = \frac{1 ^ 1 \times 2 ^ 2 \times 3 ^ 4 \times (2 ^ 2) ^ 4 \times 5 ^ 5}{1 \times (1 \times 2) \times (1 \times 2 \times 3) \times (1 \times 2 \times 3 \times 2 ^ 2) \times (1 \times 2 \times 3 \times 2 ^ 2 \times 5)} =$$

$$= \frac{1 ^ 1 \times 2 ^ {10} \times 3 ^ 3 \times 5 ^ 5}{1 ^ 5 \times 2 ^ 8 \times 3 ^ 3 \times 5 ^ 1} = 2 ^ 2 \times 5 ^ 4$$

$$D(5) = \sigma(2 ^ 2) \times \sigma(5 ^ 4) = \frac{2 ^ {2 + 1} - 1}{2 - 1} \times \frac{5 ^ {4 + 1} - 1}{5 - 1} = \frac{7}{1} \times \frac{3124}{4} = 7 \times 781 = 5467$$


```{r, message = FALSE}
library(microbenchmark)
library(bit64)
setwd("../../")
source("euler/R/primes.R")
source("euler/R/numbers.R")
options(scipen = 20)
```

```{r}
compute <- function(n, m=1000000007) {
    result <- as.integer64(rep(1, n))
    for (prime in prime_numbers(n)) {
        p <- as.integer64(prime)
        past_super <- 0; last_super <- 0; new_super <- 0; last_hyper <- 0; new_hyper <- 0
        inv_mod <- invmod(p - 1, m)
        for (i in prime:n) {
            number <- i; j <- 0
            while (number %% prime == 0) {
                j <- j + 1
                number <- number %/% prime
            }
            new_super <- last_super + j; new_hyper <- last_hyper + i * j
            last_super <- last_super + past_super; past_super <- last_super
            divisors <- ((powmod(p, last_hyper - last_super + 1, m) - 1) * inv_mod) %% m
            result[i - 1] <- (result[i - 1] * divisors) %% m
            last_super <- new_super; last_hyper <- new_hyper
        }
        divisors <- ((powmod(p, new_hyper - new_super - past_super + 1, m) - 1) * inv_mod) %% m
        result[n] <- (result[n] * divisors) %% m
    }
    return(sum(result) %% m)
}
```

```{r}
compute(5)
```
```{r}
compute(10)
```
```{r}
compute(100)
```
```{r}
compute(20000)
```

```{r}
microbenchmark(compute(2000), times = 1)
```