---
title: "Problem 700"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Eulercoin

Leonhard Euler was born on 15 April 1707.

Consider the sequence $1504170715041707n \mod 4503599627370517$.

An element of this sequence is defined to be an Eulercoin if it is strictly smaller than all previously found Eulercoins.

For example, the first term is $1504170715041707$ which is the first Eulercoin. The second term is $3008341430083414$ which is greater than $1504170715041707$ so is not an Eulercoin. However, the third term is $8912517754604$ which is small enough to be a new Eulercoin.

The sum of the first $2$ Eulercoins is therefore $1513083232796311$.

Find the sum of all Eulercoins.

## Solution
```{r, message = FALSE}
library(microbenchmark)
library(bit64)
```
```{r}
compute <- function() {
    min_value <- as.integer64(1504170715041707); max_value <- as.integer64(1504170715041707)
    modulo <- as.integer64(4503599627370517); result <- as.integer64(1504170715041707)
    candidate <- 0
    while (candidate != 1) {
        candidate <- (min_value + max_value) %% modulo
        if (candidate > max_value) {
            max_value <- candidate
        } else if (candidate < min_value) {
            min_value <- candidate
            result <- result + candidate
        }
    }
    return(result)
}
```
```{r}
compute()
```
```{r}
microbenchmark(compute())
```
