---
title: "Problem 53"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Combinatorics selections

There are exactly ten ways of selecting three from five, $12345$:

$123, 124, 125, 134, 135, 145, 234, 235, 245$, and $345$

In combinatorics, we use the notation, $\binom{5}{3} = 10$

In general, $\binom{n}{r} = \frac{n!}{r! (n - r)!}$, where $r \le n$, $n! = n \times (n - 1) \times ... \times 3 \times 2 \times 1$, and $0! = 1$.

It is not until $n = 23$, that a value exceeds one-million: $\binom{23}{10} = 1144066$.

How many, not necessarily distinct, values of $\binom{n}{r}$ for $1 \le n \le 100$, are greater than one-million?

## Solution

The first observation is $\binom{23}{10} \equiv \binom{23}{13}$. If $k = n - r$, then:

$$\binom{n}{r} = \binom{n}{k} \iff \frac{n!}{r!(n - r)!} = \frac{n!}{k!(n - k)!}$$

$$\iff \frac{n!}{r!(n - r)!} = \frac{n!}{(n - r)!(n - (n - r))!} = \frac{n!}{(n - r)!r!}$$

The second observation:

$$\binom{n}{\lfloor \frac{n}{2} \rfloor - 1} < \binom{n}{\frac{n}{2}} > \binom{n}{\lceil \frac{n}{2} \rceil + 1}$$

So we need to get only first $r$ which with $n$ would be more than one-million.

For getting binomial coefficient we'd use the [Stirling's approximation](https://en.wikipedia.org/wiki/Stirling%27s_approximation):

$$n! \sim \sqrt{2 \pi n} \left(\frac{n}{e}\right)^n$$

$$\frac{n!}{k! (n-k)!} \approx \frac{\sqrt{2 \pi n} \left(\frac{n}{e}\right)^n}{\sqrt{2 \pi k} \left(\frac{k}{e}\right)^k \sqrt{2 \pi \left(n - k \right)} \left(\frac{n - k}{e}\right)^{n - k}} = $$

$$= \frac{n^{n + \frac{1}{2}}}{\sqrt{2 \pi} k^{k + \frac{1}{2}} \left(n - k \right)^{n - k + \frac{1}{2}}} = \frac{n^k \left(\frac{1}{k} - \frac{1}{n} \right)^{k + \frac{1}{2}}}{\sqrt{2 \pi} \left(1 - \frac{k}{n} \right)^{n + 1}}$$
```{r}
library(microbenchmark)
```
```{r}
compute <- function(n_max, limit) {
    comb_approx <- function(n, k) {
        return(n ^ (n + 0.5) / sqrt(2 * pi) / k ^ (k + 0.5) / (n - k) ^ (n - k + 0.5))
    }

    result <- 0
    for (i in seq_len(n_max)) {
        for (j in seq_len(i %/% 2)) {
            if (comb_approx(i, j) > limit) {
                result <- result + i - 2 * j + 1
                break
            }
        }
    }
    return(result)
}
```
```{r}
compute(100, 1000000)
```
```{r}
microbenchmark(compute(100, 1000000))
```
