---
title: "Problem #301"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Nim

*Nim* is a game played with heaps of stones, where two players take it turn to remove any number of stones from any heap until no stone remain.

We'll consider the three-heap normal-play version of Nim, which works as follows:
- At the start of the game there are three heaps of stones.
- On each player's turn, the player may remove any positive number of stones from any single heap.
- The first player unable to move (because no stones remain) loses.

If $(n_1, n_2, n_3)$ indicates a Nim position consisting of heaps of size $n_1$, $n_2$, and $n_3$, then there is a simple function, which you may look up or attempt to deduce for yourself, $X(n_1, n_2, n_3)$ that returns:
- zero if, with perfect strategy, the player about to move will eventually lose; or
- non-zero if, with perfect strategy, the player about to move will eventually win.

For example $X(1, 2, 3) = 0$ because, no matter what the current player does, the opponent can respond with a move that leaves two heaps of equal size, at which point every move by the current player can be mirrored by the opponent until no stones remain; so the current player loses. To ilustrate:
- current player moves to $(1, 2, 1)$
- opponent moves to $(1, 0, 1)$
- current player moves to $(0, 0, 1)$
- opponent moves to $(0, 0, 0)$, and so wins.

For how many positive integers $n \le 2^{30}$ does $X(n, 2n, 3n) = 0$?

OEIS Sequence [A003714](https://oeis.org/A003714)

# Solution

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/calculus.R")
```

```{r}
compute <- function(n) get_fibonacci(n + 2)
```

```{r}
compute(30)
```

```{r}
microbenchmark(compute(30))
```