---
title: "Problem 42"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Coded triangle numbers

The $n^{th}$ term of the sequence of triangle numbers is given by, $t_n = \frac{n (n + 1)}{2}$; so the first ten triangle numbers are:

$$1, 3, 6, 10, 15, 21, 28, 36, 45, 55, ...$$

By converting each letter in a word to a number corresponding to its alphabetical position and adding these values we form a word value. For example, the word value for SKY is $19 + 11 + 25 = 55 = t_{10}$. If the word value is a triangle number then we shall call the word a triangle word.

Using [words.txt](https://projecteuler.net/project/resources/p042_words.txt) (right click and 'Save Link/Target As...'), a 16K text file containing nearly two-thousand common English words, how many are triangle words?

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function(string) {
    triangles <- 1L

    add_triangle <- function() {
        n <- length(triangles)
        triangles <<- c(triangles, n * (n + 1) / 2)
    }

    triangle_words <- 0

    for (name in string) {
        value <- sum(utf8ToInt(name) - utf8ToInt("A") + 1)
        while (value > max(triangles)) {
            add_triangle()
        }
        if (value %in% triangles) {
            triangle_words <- triangle_words + 1
        }
    }
    return(triangle_words)
}
```
```{r}
words <- strsplit(gsub("\"", "", readLines("p042_words.txt", warn = FALSE)), ",")[[1]]
```
```{r}
compute(words)
```
```{r}
microbenchmark(compute(words))
```
