---
title: "Problem 99"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Largest exponential

Comparing two numbers written in index form like $2 ^ {11}$ and $3 ^ 7$ is not difficult, as any calculator would confirm that $2 ^ {11} = 2048 < 3 ^ 7 = 2187$.

However, confirming that $632382 ^ {518061} > 519432 ^ {525806}$ would be much more difficult, as both numbers contain over three million digits.

Using [base_exp.txt](https://projecteuler.net/project/resources/p099_base_exp.txt) (right click and 'Save Link/Target As...'), a 22K text file containing one thousand lines with a base/exponent pair on each line, determine which line number has the greatest numerical value.

**NOTE**: The first two lines in the file represent the numbers in the example given above.

## Solution

It can be confirmed that $a ^ b > c ^ d$ when $bn \log_n a > dn \log_n c$. For example:

$$632282 ^ {518061} < 519432 ^ {525806}$$

$$\iff 10 \times 518061 \log 632282 < 10 \times 525806 \log 519432$$

$$\iff 518061 \log 632282 < 525806 \log 519432$$

$$\iff 518061 \times 5.800911 < 525806 \times 5.715529$$

$$\iff 3005226 < 3005259$$
```{r}
library(microbenchmark)
```

```{r}
compute <- function(path) {
    base_exp <- lapply(strsplit(readLines(path, warn = FALSE), ","), as.integer)
    max_exponent <- 0
    result <- 0
    for (i in seq_along(base_exp)) {
        exponent <- log10(base_exp[[i]][1]) * base_exp[[i]][2]
        if (exponent > max_exponent) {
            max_exponent <- exponent
            result <- i
        }
    }
    return(result)
}
```

```{r}
compute("p099_base_exp.txt")
```

```{r}
microbenchmark(compute("p099_base_exp.txt"))
```