---
title: "Problem 684"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Inverse Digit Sum

Define $s(n)$ to be the smallest number that has digit sum of $n$. For example $s(10) = 19$

Let $S(k) = \displaystyle\sum_{n=1}^k s(n)$. You are given $S(20) = 1074$.

Further, let $f_i$ be the Fibonacci sequence defined by $f_0 = 0$, $f_1 = 1$ and $f_i = f_{i - 2} + f_{i - 1}$ for all $i \ge 2$.

Find $\displaystyle\sum_{i = 2}^{90} S(f_i)$. Give your answer modulo $1000000007$.

OEIS Sequence: [A051885](https://oeis.org/A051885)

## Solution

The smallest numbers whose sum of digits is $n$, are numbers of the form $10 ^ j a - 1$ with $a \in (1, 9)$ and $j \ge 0$.

This solution uses the following formula:

$$\sum_{j=0}^b 10 ^ j a - 1 = \frac{10 ^ {b + 1}a - a - 9b - 9}{9}$$

By letting $a = (1, 9)$, we get:

$$R(k) = \sum _ {a = 1} ^ 9 \sum _ {j = 0} ^ b 10 ^ j a - 1 = 2 (2 ^ b 5 ^ {b + 2} - 7) - 9b$$

From $R(k)$, we get $S(k)$ as:

$$S(k) = R(k) - \sum _ {j = 2 + (k \mod 9)} ^ 9 10 ^ b j - 1 = R(k) - \frac{(10 - a) (10 ^ b (a + 9) - 2)}{2}$$

Simplifying the formula, we get:

$$S(k) = \frac{10 ^ b(a (a - 1) + 10) - 2 (a + 9b + 4)}{2}$$

where:

$$a = k \mod 9 + 2$$

$$b = \lfloor \frac{k}{9} \rfloor$$
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/big_int.R")
source("euler/R/calculus.R")
source("euler/R/numbers.R")
```

```{r}
compute <- function(n, m) {
    inverted_modulo <- invmod(2, m)
    result <- as.bigint(0)
    for (f in fibonacci_numbers(n)) {
        a <- f %% 9 + 2; b <- f %/% 9
        result %+=% (((a * (a - 1) + 10) * pow(as.bigint(10), b, m) - (a + b * 9 + 4) * 2) * inverted_modulo) %% m
    }
    return(result %% m - 1)
}
```

```{r}
compute(90, 1000000007)
```
```{r}
microbenchmark(compute(90, 1000000007))
```