---
title: "Problem 30"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Digit fifth powers

Surprisingly there are only three numbers that can be written as the sum of fourth powers of their digits:

$$1634 = 1^4 + 6^4 + 3^4 + 4^4$$

$$8208 = 8^4 + 2^4 + 0^4 + 8^4$$

$$9474 = 9^4 + 4^4 + 7^4 + 4^4$$

As $1 = 1^4$ is not a sum it is not included.

The sum of these numbers is $1634 + 8208 + 9474 = 19316$.

Find the sum of all the numbers that can be written as the sum of fifth powers of their digits.

## Solution

Firstly we need to find the max number that can be represented as fifth powers of number. As max digit is $9$, then we need to check if number of digits of that number $9^5n$ less or equal to $n$. So for fifth power $n = 6$, eg $\sum^n_{i=1}9^5$ is $6$-digit number but for $n = 7$ number would be still $6$-digit.

Then we just need to find the all combinations with replacements for each $n$ from $2$ (as $1^n$ isn't sum) to $6$ digits. So we don't need to check both $98$ and $89$ 'coz the sum of fifth powers their digits are equal.
```{r}
library(arrangements)
library(microbenchmark)
```
```{r}
compute <- function(n) {
    max_len <- 2
    result <- 0
    while (nchar(as.character(max_len * 9 ^ n)) >= max_len) {
        combs <- combinations(0:9, max_len, replace = TRUE)
        for (i in seq_len(nrow(combs))) {
            candidate <- 0
            for (j in seq_len(max_len)) {
                candidate <- candidate + combs[i, j] ^ n
            }
            candidate_digits <- sort(as.integer(strsplit(as.character(candidate), NULL)[[1]]))
            if (length(candidate_digits) == max_len) {
                if (sum(candidate_digits == sort(combs[i,])) == max_len) {
                    result <- result + candidate
                }
            }
        }
        max_len <- max_len + 1
    }
    return(result)
}
```
```{r}
compute(4)
```
```{r}
compute(5)
```
```{r}
microbenchmark(compute(5))
```
