---
title: "Problem 21"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Amicable numbers

Let $d(n)$ be defined as the sum of proper divisors of $n$ (numbers less than $n$ which divide evenly into $n$).

If $d(a) = b$ and $d(b) = a$, where $a \ne b$, then $a$ and $b$ are an amicable pair and each of $a$ and $b$ are called amicable numbers.

For example, the proper divisors of $220$ are $1, 2, 4, 5, 10, 11, 20, 22, 44, 55$ and $110$; therefore $d(220) = 284$. The proper divisors of $284$ are $1, 2, 4, 71$ and $142$; so $d(284) = 220$.

Evaluate the sum of all the amicable numbers under $10000$.

## Solution
```{r}
library(microbenchmark)
source("../../euler/R/primes.R")
source("../../euler/R/numbers.R")
```
```{r}
compute <- function(n) {
    sum_factors <- rep(0, n)
    primes <- get_primes(as.integer(sqrt(n)))
    result <- 0
    for (i in seq_len(n)) {
        sum_factors[i] <- sum_proper_factors(i, primes)
    }
    for (i in 2:n) {
        j <- sum_factors[i]
        if ((j != i) & (j <= n) & (sum_factors[j] == i)) {
            result <- result + i
        }
    }
    return(result)
}
```
```{r}
compute(1000)
```
```{r}
compute(10000)
```
```{r}
microbenchmark(compute(10000))
```
