---
title: "Problem 58"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Spiral primes

Starting with $1$ and spiralling anticlockwise in the following way, a square spiral with side length $7$ is formed.
```
37 36 35 34 33 32 31
38 17 16 15 14 13 30
39 18  5  4  3 12 29
40 19  6  1  2 11 28
41 20  7  8  9 10 27
42 21 22 23 24 25 26
43 44 45 46 47 48 49
```
It is interesting to note that the odd squares lie along the bottom right diagonal, but what is more interesting is that $8$ out of the $13$ numbers lying along both diagonals are prime; that is, a ratio of $\frac{8}{13} \approx 62\%$.

If one complete new layer is wrapped around the spiral above, a square spiral with side length $9$ will be formed. If this process is continued, what is the side length of the square spiral for which the ratio of primes along both diagonals first falls below $10\%$?

OEIS Sequence: [A200975](https://oeis.org/A200975)

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function(n) {
    is.prime <- function(x) {
        if (x == 3) {
            return(TRUE)
        }
        if (x < 14) {
            return(TRUE)
        }
        if (!((x %% 6 == 1) | (x %% 6 == 5))) {
            return(FALSE)
        }
        for (i in seq(6, max(as.integer(sqrt(x)), 6), 12)) {
            if ((x %% (i - 1) == 0) | (x %% (i + 1) == 0) | (x %% (i + 7) == 0)) {
                return(FALSE)
            }
        }
        return(TRUE)
    }
    j <- 3
    primes <- 0
    while (TRUE) {
        k <- (j - 3) * j + 3
        primes <- sum(primes, is.prime(k), is.prime(k + j - 1), is.prime(k + 2 * j - 2))
        if (primes / (2 * j - 1) < n) {
            return(j)
        }
        j <- j + 2
    }
}
```
```{r}
compute(0.1)
```
```{r}
microbenchmark(compute(0.1))
```
