---
title: "Problem #102"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Triangle containment

Three distinct points are plotted at random on a Cartesian plane, for which $-1000 \le x, y \le 1000$, such that a triangle formed.

Consider the following two triangles:

$$A(-340, 495), B(-153, -910), C(835, -947)$$

$$X(-175, 41), Y(-421, -714), Z(574, -645)$$

It can be verified that triangle $ABC$ contains the origin, whereas triangle $XYZ$ does not.

Using [triangles.txt](https://projecteuler.net/project/resources/p102_triangles.txt) (right click and 'Save Link/Target As...'), a $27$K text file containing the co-ordinates of one thousand "random" triangles, find the number of triangles for which the interior contains the origin.

<small>NOTE: The first two examples in the file represent the triangles in the example given above.</small>

## Solution

$X \in ABC$ if and only if $A(ABC) = A(ABX) + A(AXC) + A(XBC)$

$$A(ABC) = \left|\frac{(A_x - C_x)(B_y - A_y) - (A_x - B_x)(C_y - A_y)}{2}\right|$$

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/geometry.R")
```

```{r}
compute <- function(path) {
    triangles <- lapply(strsplit(readLines(path, warn = FALSE), ","), as.integer)
    x <- c(0, 0)
    result <- 0
    for (triangle in triangles) {
        a <- triangle[1:2]; b <- triangle[3:4]; c <- triangle[5:6]
        if (triangle_area(a, b, x) + triangle_area(a, x, c) + triangle_area(x, b, c) == triangle_area(a, b, c)) result <- result + 1
    }
    return(result)
}
```

```{r}
compute("p102_triangles.txt")
```

```{r}
microbenchmark(compute("p102_triangles.txt"))
```