---
title: "Problem 17"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Number letter counts

If the numbers $1$ to $5$ are written out in words: one, two, three, four, five, then there are $3 + 3 + 5 + 4 + 4 = 19$ letters used in total.

If all the numbers from $1$ to $1000$ (one thousand) inclusive were written out in words, how many letters would be used?

**NOTE**: Do not count spaces or hyphens. For example, $342$ (three hundred and forty-two) contains $23$ letters and $115$ (one hundred and fifteen) contains $20$ letters. The use of "and" when writing out numbers is in compliance with British usage.
## Solution
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/math.R")
```
```{r}
compute <- function(number) {
    numbers_below_10 <- nchar(c("", "one", "two", "three", "four", "five", "six", "seven", "eight", "nine"))
    numbers_below_20 <- nchar(c("ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", "seventeen",
                                "eighteen", "nineteen"))
    tenth <- nchar(c("twenty", "thirty", "forty", "fifty", "sixty", "seventy", "eighty", "ninety"))
    sum_numbers_below_10 <- sum(numbers_below_10); sum_numbers_below_20 <- sum(numbers_below_20)
    sum_tenths <- sum(tenth)
    sum_hundreds <- nchar("hundred")
    sum_and <- nchar("and")
    sum_thousands <- nchar("thousand")
    thousands <- number %/% 1000; hundreds <- number %% 1000 %/% 100
    tenths <- number %% 100 %/% 10; digits <- number %% 10
    sum_numbers_below_10 <- 190 * thousands * sum_numbers_below_10 +
        1000 * sum(numbers_below_10[1:thousands]) +
        ifelse(thousands > 0, (100 * hundreds + 10 * tenths + digits + 1) * numbers_below_10[thousands + 1], 0) +
        100 * sum(numbers_below_10[1:hundreds]) +
        ifelse(hundreds > 0, (10 * tenths + digits + 1) * numbers_below_10[hundreds + 1], 0) +
        9 * hundreds * sum_numbers_below_10 +
        ifelse(tenths != 1, fast_max((tenths - 1) * sum_numbers_below_10, 0) +
            sum(numbers_below_10[1:(digits + 1)]), sum_numbers_below_10)
    sum_numbers_below_20 <- 10 * thousands * sum_numbers_below_20 +
        hundreds * sum_numbers_below_20 +
        ifelse(tenths > 1, sum_numbers_below_20, 0) +
        ifelse(tenths == 1, sum(numbers_below_20[1:digits]), 0)
    sum_tenths <- 100 * thousands * sum_tenths + 10 * hundreds * sum_tenths +
        ifelse(tenths > 2, 10 * sum(tenth[1:(tenths - 2)]), 0) +
        ifelse(tenths == 2 | tenths == 9, (digits + 1) * tenth[tenths - 1], 0)
    sum_hundreds <- 900 * thousands * sum_hundreds + fast_max(100 * (hundreds - 1) * sum_hundreds, 0) +
        ifelse(hundreds > 0, (10 * tenths + digits + 1) * sum_hundreds, 0)
    sum_and <- 891 * thousands * sum_and + fast_max(99 * (hundreds - 1) * sum_and, 0) +
        ifelse(hundreds > 0, (10 * tenths + digits) * sum_and, 0)
    sum_thousands <- fast_max(1000 * (thousands - 1), 0) +
        ifelse(thousands > 0, (100 * hundreds + 10 * tenths + digits + 1) * sum_thousands, 0)
    return(sum_numbers_below_10 + sum_numbers_below_20 + sum_tenths + sum_hundreds + sum_and + sum_thousands)
}
```
```{r}
compute(5)
```
```{r}
compute(1000)
```
```{r}
microbenchmark(compute(1000))
```
