---
title: "Problem 5"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Smallest multiple
$2520$ is the smallest number that can be divided by each of the numbers from $1$ to $10$ without any remainder. What is the smallest positive number that is *evenly divisible* by all of the numbers from $1$ to $20$.

## Solution
Let's look at example.

$$2520=8\times9\times5\times7=2^3\times3^2\times5^1\times7^1$$

$8$ divisible by $2, 4, 8$; $9$ divisible by $3, 9$. And if number divisible by $2$ and $3$ then number divisible by $6$. Also if number divisible by $2$ and $5$ then number divisible by $10$. So we need only prime numbers and max power that less or equal $n$.

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```

```{r}
compute <- function(n) {
    primes <- get_primes(n)
    return(prod(primes ^ as.integer(log(n, primes))))
}
```

```{r}
compute(10)
```

```{r}
compute(20)
```

```{r}
microbenchmark(compute(20))
```
