---
title: "Problem 1"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

# Problem 1
## Multiples of 3 and 5
##### If we list all the natural numbers below $10$ that are multiples of $3$ or $5$, we get $3, 5, 6$ and $9$. The sum of these multiples is $23$. Find the sum of all the multiples of $3$ or $5$ below $1000$.
## Solution
##### Have a look at all numbers below $10$ that are multiplies of $3$: $3, 6, 9$. It's just arithmetic progression. So we could use the formula of the sum of first $n$ terms of sequence for this problem:
$$\sum_{i=1}^{n}a_i=S_n=\frac{n(a_{1}+a_{n})}{2}=\frac{n(2a_1+d(n-1))}{2}$$

##### Where $a_1, a_n$ the first and the last terms in the sequence. And $d$ the common difference.
##### Considering sequence with common difference of $3$ below $10$. For getting number of terms we just need Euclidean division of $10-1$ by $3$. Quotient would be needed value.
##### Thus the first term of sequence $a_1=3$, common difference also $3$: $d=3$ and $n=\lfloor\frac{10-1}{3}\rfloor=3$. Thus $S_n=18$.
##### So we've two arithmetic sequence but they produce common numbers. Have a look at sequences $3, 6, 9, 12, 15, 18, 21, 24, 27, 30$ and $5, 10, 15, 20, 25, 30$. As you might have noticed the $15$ and $30$ are in both sequences. And this is also start of third arithmetic sequence with common difference $3\times5=15$. So for right solution we need to subtract sum of third arithmetic sequence.

```{r}
library(microbenchmark)
source("../euler/R/calculus.R")
```
```{r}
compute <- function(a, b, n) {
  n <- n - 1
  return(sum(sum_arithmetic_series(a, a, n %/% a),
             sum_arithmetic_series(b, b, n %/% b),
             - sum_arithmetic_series(a * b, a * b, n %/% (a * b))))
}
```
```{r}
compute(3, 5, 10)
```
```{r}
compute(3, 5, 1000)
```
```{r}
microbenchmark(compute(3, 5, 1000))
```
