---
title: "Problem #74"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Digit factorial chains

The number $145$ is well known for the property that the sum of the factorial of its digits is equal to $145$:

$$1! + 4! + 5! = 1 + 24 + 120 = 145$$

Perhaps less well known is $169$, in that it produces the longest chains of numbers that link back to $169$; it turns out that there are only three such loops that exist:

$$169 \to 363601 \to 1454 \to 169$$

$$871 \to 45361 \to 871$$

$$872 \to 45362 \to 872$$

It is not difficult to prove that EVERY starting number will eventually get stuck in a loop. For example,

$$69 \to 363600 \to 1454 \to 169 \to 363601 (\to 1454)$$

$$78 \to 45360 \to 871 \to 45361 (\to 871)$$

$$540 \to 145 (\to 145)$$

Starting with $69$ produces a chain of five non-repeating terms, but the longest non-repeating chain with a starting number below one million is sixty terms.

How many chains, with a starting number below one million, contain exactly sixty non-repeating terms?

## Solution
```{r}
library(microbenchmark)
library(arrangements)
```

```{r}
compute <- function(n, m) {
    get_next_term <- function(k) {
        return(sum(factorials[as.integer(strsplit(as.character(k), "")[[1]]) + 1]))
    }
    get_chain_len <- function(k) {
        if (!(is.na(chains[k]))) {
            return(chains[k])
        }
        term <- k
        chain <- term
        term <- get_next_term(term)
        while (!any(chain == term)) {
            chain <- c(chain, term)
            if (!is.na(chains[term])) {
                break
            }
            term <- get_next_term(term)
        }
        index_term <- which(chain == term)
        loop_len <- ifelse(!is.na(chains[term]), chains[term], length(chain) - index_term + 1)
        for (i in seq_along(chain)) {
            if (i >= index_term) {
                chains[chain[i]] <<- loop_len
            } else {
                chains[chain[i]] <<- index_term - i + loop_len
            }
        }
        return(chains[k])
    }
    factorials <- factorial(0:9)
    chains <- 1
    result <- 0
    combs <- combinations(9:0, n, replace = TRUE)
    for (i in seq_len(nrow(combs) - 1)) {
        combination <- combs[i, ]
        for (j in seq_len(sum(combination == 0) + 1)) {
            if (get_chain_len(as.integer(paste0(combination, collapse = ""))) == m) {
                n_digits <- length(combination)
                n_zeros <- sum(combination == 0)
                counter <- table(combination)
                result <- result + (n_digits - n_zeros) * factorials[n_digits] / prod(factorials[counter + 1])
            }
            if (any(combination == 0)) {
                combination <- combination[-match(0, combination)]
            }
        }
    }
    return(result)
}
```

```{r}
compute(6, 60)
```

```{r}
microbenchmark(compute(6, 60))
```