---
title: "Problem #112"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Bouncy numbers

Working from left-to-right if no digit is exceeded by the digit to its left it is called an increasing number; for example $134468$.

Similarly if no digit is exceeded by the digit to its right it is called a decreasing number; for example, $66420$.

We shall call a positive integer that is neither increasing nor decreasing a "bouncy" number; for example, $155349$.

Clearly there cannot be any bouncy numbers below one-hundred, but just over half of the numbers below one-thousand ($525$) are bouncy. In fact, the least number for which the proportion of bouncy numbers first reaches $50\%$ is $538$.

Surprisingly, bouncy numbers become more and more common and by the time we reach $21780$ the proportion of bouncy numbers is equal to $90\%$.

Find the least number for which the proportion of bouncy numbers is exactly $99\%$.

## Solution

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/numbers.R")
options(scipen = 20)
```

```{r}
compute <- function(n) {
    bouncy <- 0
    i <- 1
    while (bouncy / i < n) {
        i <- i + 1
        digits <- get_digits(i)
        sorted_digits <- sort(digits)
        if (!(all(digits == sorted_digits) || all(digits == rev(sorted_digits)))) bouncy <- bouncy + 1
    }
    return(i)
}
```

```{r}
compute(0.5)
```
```{r}
compute(0.9)
```
```{r}
compute(0.99)
```

```{r}
microbenchmark(compute(0.99))
```