---
title: "Problem 67"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Maximum path sum II
By starting at the top of the triangle below and moving to adjacent numbers on the row below, the maximum total from top to bottom is $23$.

```
   3
  7 4
 2 4 6
8 5 9 3
```

That is, $3 + 7 + 4 + 9 = 23$.

Find the maximum total from top to bottom in [triangle.txt](https://projecteuler.net/project/resources/p067_triangle.txt) (right click and 'Save Link/Target As...'), a 15K text file containing a triangle with one-hundred rows.

**NOTE**: This is a much more difficult version of [Problem 18](https://projecteuler.net/problem=18). It is not possible to try every route to solve this problem, as there are $2^{99}$ altogether! If you could check one trillion ($10^{12}$) routes every second it would take over twenty billion years to check them all. There is an efficient algorithm to solve it. ;o)

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function(triangle) {
    while (length(triangle) > 1) {
        len <- length(triangle)
        for (i in seq_len(len - 1)) {
            triangle[[len - 1]][i] <- triangle[[len - 1]][i] + max(triangle[[len]][i:(i + 1)])
        }
        triangle <- triangle[-len]
    }
    return(triangle[[1]])
}
```
```{r}
triangle_file <- lapply(strsplit(gsub("\"", "", readLines("p067_triangle.txt", warn = FALSE)), " "), as.integer)
```
```{r}
compute(triangle_file)
```
```{r}
microbenchmark(compute(triangle_file))
```
