---
title: "Problem 24"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Lexicographic permutations

A permutation is an ordered arrangement of objects. For example, 3124 is one possible permutation of the digits $1, 2, 3$ and $4$. If all of the permutations are listed numerically or alphabetically, we call it lexicographic order. The lexicographic permutations of $0, 1$ and $2$ are:

$$012, 021, 102, 120, 201, 210$$

What is the millionth lexicographic permutation of the digits $0, 1, 2, 3, 4, 5, 6, 7, 8$ and $9$?

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function(n, digits) {
    l <- length(digits)
    result <- ""
    remain <- n - 1
    for (i in seq_len(l)) {
        order <- factorial(l - i)
        j <- remain %/% order + 1
        result <- paste0(result, digits[j])
        remain <- remain %% order
        digits <- digits[-j]
    }
    return(result)
}
```
```{r}
compute(6, 0:2)
```
```{r}
compute(1000000, 0:9)
```
```{r}
microbenchmark(compute(1000000, 0:9))
```
