---
title: "Problem #65"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Convergents of $e$

The square root of $2$ can be written as an infinite continued fraction.

$$\sqrt{2} = 1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2 + ...}}}}$$

The infinite continued fraction can be written, $\sqrt{2} = [1; (2)]$, $(2)$ indicates that $2$ repeats *ad infinitum*. In a similar way, $\sqrt{23} = [4; (1, 3, 1, 8)]$.

It turns out that the sequence of partial values of continued fractions for square roots provide the best rational approximations. Let us consider the convergents for $\sqrt{2}$.

$$1 + \frac{1}{2} = \frac{3}{2}$$

$$1 + \frac{1}{2 + \frac{1}{2}} = \frac{7}{5}$$

$$1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2}}} = \frac{17}{12}$$

$$1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2}}}} = \frac{41}{29}$$

Hence the sequence of the first ten convergents for $\sqrt{2}$ are:

$$1, \frac{3}{2}, \frac{7}{5}, \frac{17}{12}, \frac{41}{29}, \frac{99}{70}, \frac{239}{169}, \frac{577}{408}, \frac{1393}{985}, \frac{3363}{2378}, ...$$

What is most surprising is that the important mathematical constant, $e = [2, 1, 2, 1, 1, 4, 1, 1, 6, 1, ..., 1, 2k, 1, ...]$.

The first ten terms in the sequence of convergents for $e$ are:

$$2, 3, \frac{8}{3}, \frac{11}{4}, \frac{19}{7}, \frac{87}{32}, \frac{106}{39}, \frac{193}{71}, \frac{1264}{465}, \frac{1457}{536}, ...$$

The sum of digits in the numerator of the $10$<sup>th</sup> convergent is $1 + 4 + 5 + 7 = 17$.

Find the sum of digits in the numerator of the $100$<sup>th</sup> convergent of the continued fraction for $e$.

OEIS Sequence: [A113873](https://oeis.org/A113873)

## Solution

$$f(3n) = f(3n - 1) + f(3n - 2)$$

$$f(3n + 1) = 2n \times f(3n) + f(3n - 1)$$

$$f(3n + 2) = f(3n + 1) + f(3n)$$
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/big_int.R")
source("euler/R/numbers.R")
```

```{r}
compute <- function(n) {
    current <- as.bigint(1); previous <- as.bigint(1)
    for (i in seq(2, n + 1)) {
        temp <- current
        if (i %% 3 == 1) current <- current * as.bigint(2 * i %/% 3)
        current <- current + previous; previous <- temp
    }
    return(digits_sum(current))
}
```

```{r}
compute(10)
```
```{r}
compute(100)
```

```{r}
microbenchmark(compute(100))
```