---
title: "Problem 28"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Number spiral diagonals

Starting with the number $1$ and moving to the right in a clockwise direction a 5 by 5 spiral is formed as follows:

```
21, 22, 23, 24, 25
20,  7,  8,  9, 10
19,  6,  1,  2, 11
18,  5,  4,  3, 12
17, 16, 15, 14, 13
```
It can be verified that the sum of the numbers on the diagonals is $101$.

What is the sum of the numbers on the diagonals in a $1001$ by $1001$ spiral formed in the same way?

## Solution

Considering on $4$ diagonals we'll get $4$ sequences:

$$a_n = (9, 25, 49, 81, 121, 169, 225...) = 4n^2 + 4n + 1$$

$$b_n = (7, 21, 43, 73, 111, 157, 211...) = 4n^2 + 2n + 1$$

$$c_n = (5, 17, 37, 65, 101, 145, 197...) = 4n^2 + 1$$

$$d_n = (3, 13, 31, 59, 91, 132, 183...) = 4n^2 - 2n + 1$$

For answer we need just find sum of these sequences plus $1$ for middle element.

$$s_n = 1 + \sum^n_{i=1}(a_i + b_i + c_i + d_i) = $$

$$= 1 + \sum^n_{i=1}(4i^2 + 4i + 1 + 4i^2 + 2i + 1 + 4i^2 + 1 + 4i^2 - 2i + 1) = 1 + \sum^n_{i=1}(16i^2 + 4i+ 4) =$$

$$= 1 + 16\sum^n_{i=1}i^2 + 4\sum^n_{i=1}i + \sum^n_{i=1}4 = 1 + \frac{8n(n + 1)(2n + 1)}{3} + 2n(n + 1) + 4n =$$

$$= 1 + \frac{2n(8n^2 + 15n + 13)}{3}$$

Since we divided diagonals by two and excluded middle element our need looks like $n = \frac{N - 1}{2}$ where $N$ is size of spiral.

At the last we could simplify solution using [Horner's method](https://en.wikipedia.org/wiki/Horner%27s_method):

$$1 + \frac{\left(N - 1\right)\left(8\left(\frac{N - 1}{2}\right)^2 + 15\frac{N - 1}{2} + 13\right)}{3} = \frac{n \left(n \left(4n + 3\right) + 8\right) - 9}{6}$$
```{r}
library(microbenchmark)
```
```{r}
compute <- function(n) {
    return((((4 * n + 3) * n + 8) * n - 9) / 6)
}
```
```{r}
compute(5)
```
```{r}
compute(1001)
```
```{r}
microbenchmark(compute(1001))
```
