---
title: "Problem #85"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Counting rectangles

By counting carefully it can be seen that a rectangular grid measuring $3$ by $2$ contains eighteen rectangles:

<center><img src = 'https://projecteuler.net/project/images/p085.png' title = 'Counting rectangles'></center><br/>

Although there exists no rectangular grid that contains exactly two million rectangles, find the area of the grid with the nearest solution.

OEIS Sequences [A000217](https://oeis.org/A000217), [A096948](https://oeis.org/A096948)

## Solution

Let $f(n)$ number of rectangles in $1 \times n$ rectangle and $F(n, m)$ number of rectangles in $n \times m$ rectangle.

$$f(n) = \frac{n(n + 1)}{2}$$

$$F(n, m) = f(n) \times f(m)$$
```{r}
library(microbenchmark)
```

```{r}
compute <- function(n) {
    limit <- as.integer(sqrt(n))
    triangles <- 1
    for (i in 2:limit) {
        triangles[i] <- triangles[i - 1] + i
    }
    min_difference <- n
    nearest <- 0
    for (i in seq_len(limit)) {
        for (j in seq_len(i)) {
            rectangles <- triangles[i] * triangles[j]
            difference <- abs(n - rectangles)
            if (difference < min_difference) {
                min_difference <- difference
                nearest <- i * j
            }
            if (rectangles > n) {
                break
            }
        }
    }
    return(nearest)
}
```

```{r}
compute(18)
```
```{r}
compute(2000000)
```

```{r}
microbenchmark(compute(2000000))
```