---
title: "Problem 69"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Totient maximum

Euler's Totient function, $\phi(n)$ [sometimes called the phi function], is used to determine the number of numbers less than $n$ which are relatively prime to $n$. For example, as $1$, $2$, $4$, $5$, $7$, and $8$, are all less than nine and relatively prime to nine, $\phi(9) = 6$.

$n$ | Relatively Prime | $\phi(n)$ | $\frac{n}{\phi(n)}$
:-: | :-: | :-: | :-:
$2$ | $1$ | $1$ | $2$ | $2$
$3$ | $1$, $2$ | $2$ | $1.5$
$4$ | $1$, $3$ | $2$ | $2$
$5$ | $1$, $2$, $3$, $4$ | $4$ | $1.25$
$6$ | $1$, $5$ | $2$ | $3$
$7$ | $1$, $2$, $3$, $4$, $5$, $6$ | $6$ | $1.1(6)$
$8$ | $1$, $3$, $5$, $7$ | $4$ | $2$
$9$ | $1$, $2$, $4$, $5$, $7$, $8$ | $6$ | $1.5$
$10$ | $1$, $3$, $7$, $9$ | $4$ | $2.5$

It can be seen that $n = 6$ produces a maximum $\frac{n}{\phi(n)}$ for $n \le 10$.

Find the value of $n \le 1000000$ for which $\frac{n}{\phi(n)}$ is a maximum.

OEIS Sequence: [A000010](https://oeis.org/A000010)

## Solution

Euler's Totient function can be defined with [formula](https://en.wikipedia.org/wiki/Euler's_totient_function):

$$\phi(n) = n \prod_{p | n} \left(1 - \frac{1}{p} \right)$$

So basically that means we are trying to maximize the following function:

$$\frac{n}{\phi(n)} = \frac{n}{n \displaystyle\prod_{p | n} \left(1 - \frac{1}{p} \right)} = \frac{1}{\displaystyle\prod_{p | n} \left(1 - \frac{1}{p} \right)} = \prod_{p | n} \frac{p}{p - 1}$$

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```

```{r}
compute <- function(n) {
    result <- 1
    for (prime in get_primes(sqrt(n))) {
        result <- result * prime
        if (result * prime > n) {
            return(result)
        }
    }
}
```

```{r}
compute(10)
```
```{r}
compute(1000000)
```

```{r}
microbenchmark(compute(1000000))
```