---
title: "Problem #205"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Dice Game

Peter has nine four-sided (pyramidal) dice, each with faces numbered $1, 2, 3, 4$.

Colin has six six-sided (cubic) dice, each with faces numbered $1, 2, 3, 4, 5, 6$.

Peter and Colin roll their dice and compare totals: the highest total wins. The result is a draw if the totals are equal.

What is the probability that Pyramidal Pete beats Cubic Colin? Give your answer rounded to seven decimal places in the form $0.abcdefg$.

## Solution

To get combinations of totals $p$ for $n$ $s$-sided dice we'll use next formula:

$$F(p, n, s) = \displaystyle\sum_{k = 0}^{\displaystyle\lfloor\frac{p - n}{s}\displaystyle\rfloor} (-1)^k \binom{n}{k} \binom{p - sk - 1}{n - 1}$$

```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/game.R")
source("euler/R/math.R")
```

```{r}
compute <- function(a, b) {
    limit <- fast_max(a[1] * a[2], b[1] * b[2])
    looses <- rep(0, limit)
    result <- 0
    for (i in b[1]:(b[1] * b[2])) looses[i] <- dice_combinations(i, b[1], b[2]) + looses[i - 1]
    for (i in a[1]:(a[1] * a[2])) result <- result + dice_combinations(i, a[1], a[2]) * looses[i - 1]
    return(round(result / a[2] ^ a[1] / b[2] ^ b[1], 7))
}
```

```{r}
compute(c(9, 4), c(6, 6))
```

```{r}
microbenchmark(compute(c(9, 4), c(6, 6)))
```