---
title: "Problem 92"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
# Problem 92
## Square digit chains

A number chain is created by continuously adding the square of the digits in a number to form a new number until it has been seen before.

For example,

$$44 \to 32 \to 13 \to 10 \to 1 \to 1$$

$$85 \to 89 \to 145 \to 42 \to 20 \to 4 \to 16 \to 37 \to 58 \to 89$$

Therefore any chain that arrives at $1$ or $89$ will become stuck in an endless loop. What is most amazing is that EVERY starting number will eventually arrive at $1$ or $89$.

How many starting numbers below ten million will arrive at $89$?

## Solution
```{r}
library(arrangements)
library(microbenchmark)
```
```{r}
compute <- function(n) {
    sum_squares_digits <- function(x) {
        return(sum(as.integer(strsplit(x, NULL)[[1]]) ^ 2))
    }

    result <- 0
    combs <- combinations(0:9, n, replace = TRUE)
    for (i in seq_len(nrow(combs))) {
        combination <- paste0(combs[i,], collapse = "")
        while (TRUE) {
            combination <- sum_squares_digits(combination)
            if (combination == 89) {
                result <- result + factorial(n) / prod(factorial(table(combs[i, ])))
                break
            } else if (combination < 2) {
                break
            } else {
                combination <- as.character(combination)
            }
        }
    }
    return(result)
}
```
```{r}
compute(7)
```
```{r}
microbenchmark(compute(7))
```
