---
title: "Problem 6"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Sum square difference
The sum of squares of the first ten natural numbers is,

$$1^2 + 2^2 + ... + 10^2 = 385$$

The square of the sum if the first ten natural numbers is,

$$(1 + 2 + ... + 10)^2 = 55^2 = 3025$$

Hence the difference between the sum of the squares of the first ten natural numbers and the square of the sum is $3025 - 385 = 2640$. Find the difference between the sum of the squares of the first one hundred natural numbers and the square of the sum.

## Solution
The sum of the square is,

$$\sum_{i=1}^ni^2=\frac{n(n+1)(2n+1)}{6}$$

The square of the sum is,

$$\left(\sum_{i=1}^ni\right)^2=\frac{n^2(n+1)^2}{4}$$

The difference is,

$$\left(\sum_{i=1}^ni^2\right)-\left(\sum_{i=1}^ni\right)^2=\frac{n(n+1)(2n+1)}{6}-\frac{n^2(n+1)^2}{4}=\frac{n(n+1)(3n^2-n-2)}{12}$$

```{r}
library(microbenchmark)
```

```{r}
compute <- function(n) {
    return(n * (n + 1) * (3 * n ^ 2 - n - 2) / 12)
}
```

```{r}
compute(10)
```

```{r}
compute(100)
```

```{r}
microbenchmark(compute(100))
```