---
title: "Problem #73"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---

## Counting fractions in a range

Consider the fraction, $\frac{n}{d}$, where $n$ and $d$ are positive integers. If $n < d$ and $HCF(n, d) = 1$, it is called a reduced proper fraction.

If we list the set of reduced proper fractions for $d \le 8$ in ascending order of size, we get:

$$\frac{1}{8}, \frac{1}{7}, \frac{1}{6}, \frac{1}{5}, \frac{1}{4}, \frac{2}{7}, \frac{1}{3}, \frac{3}{8}, \frac{2}{5}, \frac{3}{7}, \frac{1}{2}, \frac{4}{7}, \frac{3}{5}, \frac{5}{8}, \frac{2}{3}, \frac{5}{7}, \frac{3}{4}, \frac{4}{5}, \frac{5}{6}, \frac{6}{7}, \frac{7}{8}$$

It can be seen that there are $3$ fractions between $\frac{1}{3}$ and $\frac{1}{2}$.

How many fractions lie between $\frac{1}{3}$ and $\frac{1}{2}$ in the sorted set of reduced proper fractions for $d \le 12000$?

## Solution
```{r}
library(microbenchmark)
```

```{r}
compute <- function(n) {
    sieve <- rep(0, n)
    for (i in 2:n) {
        sieve[i] <- sieve[i] + i - 1 - i %/% 2 - i %/% 3
        j <- 2 * i
        while (j <= n) {
            sieve[j] <- sieve[j] - sieve[i]
            j <- j + i
        }
    }
    return(sum(sieve))
}
```

```{r}
compute(8)
```

```{r}
compute(12000)
```

```{r}
microbenchmark(compute(12000))
```