---
title: "Problem 49"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Prime permutations

The arithmetic sequence, $1487, 4817, 8147$, in which each of the terms increases by $3330$, is unusual in two ways: (i) each of the three terms are prime, and, (ii) each of the $4$-digit numbers are permutations of one another.

There are no arithmetic sequences made up of three $1$-, $2$-, or $3$-digit primes, exhibiting this property, but there is one other $4$-digit increasing sequence.

What $12$-digit number do you form by concatenating the three terms in this sequence?

## Solution
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```
```{r}
compute <- function() {
    sieve <- prime_sieve(10000)
    primes <- which(sieve)
    for (prime in primes[primes > 4817]) {
        first <- prime - 3330; third <- prime + 3330
        prime_digits <- sort(unique(utf8ToInt(as.character(prime))))
        first_digits <- sort(unique(utf8ToInt(as.character(prime))))
        third_digits <- sort(unique(utf8ToInt(as.character(prime))))
        if (sieve[first] && sieve[third] && length(prime_digits) == length(first_digits) &&
            all(prime_digits == first_digits) && length(prime_digits) == length(third_digits) &&
            all(prime_digits == third_digits)) {
            return(paste0(first, prime, third))
        }
    }
}
```
```{r}
compute()
```
```{r}
microbenchmark(compute())
```
