---
title: "Problem 71"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Ordered fractions

Consider the fraction, $\frac{n}{d}$, where $n$ and $d$ are positive integers. If $n < d$ and $HCF(n, d) = 1$, it is called a reduced proper fraction.

If we list the set of reduced proper fractions for $d \le 8$ in ascending order of size, we get:

$$\frac{1}{8}, \frac{1}{7}, \frac{1}{6}, \frac{1}{5}, \frac{1}{4}, \frac{2}{7}, \frac{1}{3}, \frac{3}{8}, \frac{\boldsymbol2}{\boldsymbol5}, \frac{3}{7}, \frac{1}{2}, \frac{4}{7}, \frac{3}{5}, \frac{5}{8}, \frac{2}{3}, \frac{5}{7}, \frac{3}{4}, \frac{4}{5}, \frac{5}{6}, \frac{6}{7}, \frac{7}{8}$$

It can be seen that $\frac{2}{5}$ is the fraction immediately to the left of $\frac{3}{7}$.

By listing the set of reduced proper fractions for $d \le 1000000$ in ascending order of size, find the numerator of the fraction immediately to the left of $\frac{3}{7}$.

## Solution
```{r}
library(microbenchmark)
```

```{r}
compute <- function(n) {
    return((n - 5) %/% 7 * 3 + 2)
}
```

```{r}
compute(8)
```
```{r}
compute(1000000)
```

```{r}
microbenchmark(compute(1000000))
```