---
title: "Problem 19"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Counting Sundays

You are given the following information, but you may prefer to do some research for yourself.
* 1 Jan 1900 was a Monday.
* Thirty days has September, April, June and November. All the rest have thirty-one, Saving February alone, Which has twenty-eight, rain or shine. And on leap years, twenty-nine.
* A leap year occurs on any year evenly divisible by $4$, but not on a century unless it is divisible by $400$.

How many Sundays fell on the first of the month during the twentieth century (1 Jan 1901 to 31 Dec 2000)?

## Solution
```{r}
library(microbenchmark)
```
```{r}
compute <- function() {
    month_days <- c(31, 0, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
    day <- 2
    result <- 0
    for (year in 1901:2000) {
        month_days[2] <- 28 + (year %% 4 == 0 && (year %% 100 != 0 ||year %% 400 == 0))
        for (month in seq_along(month_days)) {
            day <- day + month_days[month] %% 7
            if (day %% 7 == 0) result <- result + 1
        }
    }
    return(result)
}
```
```{r}
compute()
```
```{r}
microbenchmark(compute())
```
