---
title: "Problem 27"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Quadratic primes

Euler discovered the remarkable quadratic formula:

$$n^2+n+41$$

It turns out that the formula will produce $40$ primes for the consecutive integer values $0 \leq n \leq 39$. However, when $n = 40$, $40^2 + 40 + 41 = 40 \times (40 + 1) + 41$ is divisible by $41$, and certainly when $n = 41$, $41^2 + 41 + 41$ is clearly divisible by $41$.

The incredible formula $n^2 - 79 \times n + 1601$ was discovered, which produces $80$ primes for the consecutive values $0 \leq n \leq 79$. The product of the coefficients, $-79$ and $1601$, is $-126479$.

Considering quadratics of the form:

$n^2 + an + b$, where $|a| < 1000$ and $|b| \leq 1000$

where $|n|$ is the modulus / absolute value of $n$

e.g. $|11| = 11$ and $|-4| = 4$

Find the products of the coefficients, $a$ and $b$, for the quadratic expression that produces the maximum number of primes for consecutive values of $n$, starting with $n = 0$.

## Solution
Since $n^2 + an + b$ must be prime for $n_0=0$,

$$n^2_0+an_0+b=b$$

So $b$ must be prime. Also for $n_1=1$:

$$n^2_1+an_1+b=1+a+b$$.

Since $b$ is prime and all primes but $2$ are odd, it follows that $a$ must be odd for all $b\ne2$ and even for $b=2$.
```{r}
library(microbenchmark)
setwd("../../")
source("euler/R/primes.R")
```
```{r}
compute <- function(max_a, max_b) {
    prime <- prime_sieve(max_a * max_b)
    primes <- which(prime[1:max_b])
    primes <- c(primes, -primes)
    max_sequence <- 0; result <- 0
    for (a in seq(-max_a + ifelse(max_a %% 2 == 0, 1, 2), max_a - 1, 2)) {
        for (b in primes) {
            n <- 0
            while (TRUE) {
                candidate <- abs(n * (n + a) + b)
                if (candidate != 0 && !prime[candidate]) break
                n <- n + 1
            }
            if (n > max_sequence) {
                max_sequence <- n
                result <- a * b
            }
        }
    }
    return(result)
}
```
```{r}
compute(1000, 1000)
```
```{r}
microbenchmark(compute(1000, 1000))
```
