---
title: "Problem 43"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Sub-string divisibility

The number, $1406357289$, is a $0$ to $9$ pandigital number because it is made up of each of the digits $0$ to $9$ in some order, but it also has a rather interesting sub-string divisibility property.

Let $d_1$ be the $1^{st}$ digit, $d_2$ be the $2^{nd}$ digit, and so on. In this way, we note the following:

- $d_2 d_3 d_4 = 406$ is divisible by $2$
- $d_3 d_4 d_5 = 063$ is divisible by $3$
- $d_4 d_5 d_6 = 635$ is divisible by $5$
- $d_5 d_6 d_7 = 357$ is divisible by $7$
- $d_6 d_7 d_8 = 572$ is divisible by $11$
- $d_7 d_8 d_9 = 728$ is divisible by $13$
- $d_8 d_9 d_{10} = 289$ is divisible by $17$

Find the sum of all $0$ to $9$ pandigital numbers with this property.

## Solution
```{r}
library(microbenchmark)
library(arrangements)
setwd("../../")
source("euler/R/primes.R")
```
```{r}
compute <- function(n) {
    get_permutation_numbers <- function(used, prime_index) {
        sub_result <- 0
        for (i in digits[!digits %in% used]) {
            if (as.integer(paste0(c(i, used[1:2]), collapse = "")) %% primes[prime_index] == 0) {
                if (prime_index < 7) {
                    sub_result <- sub_result + get_permutation_numbers(c(i, used), prime_index + 1)
                } else {
                    used_digits <- c(i, used)
                    sub_result <- sub_result + as.numeric(paste0(c(digits[!digits %in% used_digits], used_digits), collapse = ""))
                }
            }
        }
        return(sub_result)
    }
    digits <- 0:n
    primes <- rev(prime_numbers(17))
    result <- 0
    perms <- permutations(digits, 3)
    for (i in seq_len(nrow(perms))) {
        if (as.integer(paste0(perms[i,], collapse = "")) %% primes[10 - n] == 0) {
            result <- result + get_permutation_numbers(perms[i,], 11 - n)
        }
    }

    return(result)
}
```
```{r}
compute(9)
```
```{r}
microbenchmark(compute(9))
```
