---
title: "Problem 57"
author: "Dynortice"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
---
## Square root convergents

It is possible to show that the square root of two can be expressed as an infinite continued fraction.

$$\sqrt{2} = 1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2 + ...}}}$$

By expanding this for the first four iterations, we get:

$$1 + \frac{1}{2} = \frac{3}{2} = 1.5$$

$$1 + \frac{1}{2 + \frac{1}{2}} = \frac{7}{5} = 1.4$$

$$1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2}}} = \frac{17}{12} = 1.41666...$$

$$1 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2 + \frac{1}{2}}}} = \frac{41}{29} = 1.41379...$$

The next three expansions are $\frac{99}{70}, \frac{239}{169}$ and $\frac{577}{408}$, but the eight expansion, $\frac{1393}{985}$, is the first example where the number of digits in the numerator exceeds the number of digits in the denominator.

In the first one-thousand expansions, how many fractions contain a numerator with more digits than the denominator?

## Solution

```{r}
library(microbenchmark)
setwd('../../')
source("euler/R/big_int.R")
```
```{r}
compute <- function(d, n) {
    numerator <- as.bigint(1)
    denominator <- as.bigint(1)
    a <- d
    b <- d - 1
    result <- 0
    for (i in seq_len(n)) {
        denominator_next <- numerator + denominator * b
        numerator %+=% (denominator * a)
        denominator <- denominator_next
        if (length(numerator) != length(denominator)) {
            result <- result + 1
        }
    }
    return(result)
}
```
```{r}
compute(2, 8)
```
```{r}
compute(2, 1000)
```
```{r}
microbenchmark(compute(2, 1000), times = 10)
```
